PANCHANGE_analysis

### 2020-12-04 PANCHANGE_analysis.Rmd

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "highest_education_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# SENSITIVITY based on employment status

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_estimates)
gad_prepan_model1b_employment_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employment_reg_stats)
gad_prepan_model1b_employment_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_estimates)
phq_prepan_model1b_employment_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employment_reg_stats)
phq_prepan_model1b_employment_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_estimates)
ocir_prepan_model1b_employment_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employment_reg_stats)
ocir_prepan_model1b_employment_reg_stats
```

#PCL prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employment_estimates)
pcl_prepan_model1b_employment_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "employment.unemployed_numeric",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employment_reg_stats)
pcl_prepan_model1b_employment_reg_stats
```

# SENSITIVITY based on employment change

```{r create an employment change variable}
dat.prepan <- dat.prepan %>%
  mutate(employment_change =
           case_when(
             employment.unemployed_numeric == "1" ~ "Unemployed",
             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
             key_worker_numeric == "1" ~ "Key Worker",                                            
             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
             employment.retired_numeric == "1" ~ "Retired",                                   
             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
             employment.student_university_numeric == "1" ~ "Student"                        
           )
  )

dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
```

# GAD prepan
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment change sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employmentchange_estimates)
gad_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_employmentchange_reg_stats)
gad_prepan_model1b_employmentchange_reg_stats
```

# PHQ prepan
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment change sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employmentchange_estimates)
phq_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_employmentchange_reg_stats)
phq_prepan_model1b_employmentchange_reg_stats
```

# OCIR prepan 
## Regression: Absolute scores

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment change sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employmentchange_estimates)
ocir_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_employmentchange_reg_stats)
ocir_prepan_model1b_employmentchange_reg_stats
```

#PCL prepan 
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl employment change sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employmentchange_estimates)
pcl_prepan_model1b_employmentchange_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "employment_change",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_employmentchange_reg_stats)
pcl_prepan_model1b_employmentchange_reg_stats
```

# Sensitivity based on GLAD sign up
#PCL prepan: sensitivity
## Regression: Absolute scores
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
#### Subset of participants 3 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 3 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_3months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 6 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 6 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_6months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

#### Subset of participants 9 months prior to pandemic
```{r pcl model1b sum_score prepan - sensitivity 9 months}
# Regression coefficients
pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_estimates)
pcl_prepan_model1b_explan_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan_sensitivity_9months")
kable(pcl_prepan_model1b_explan_reg_stats)
pcl_prepan_model1b_explan_reg_stats
```

>>>>

```{r model1b education function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "highest_education"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
               "highest_educationNVQ" = "Highest education NVQ",
               "highest_educationA-levels" = "Highest education A-Levels",
               "highest_educationUniversity" = "Highest education University"

```{r model1b.explan education function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "highest_education"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
               "highest_educationNVQ" = "Highest education NVQ",
               "highest_educationA-levels" = "Highest education A-Levels",
               "highest_educationUniversity" = "Highest education University"

# GAD baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# Regression diagnostic statistics
gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_reg_stats)
gad_baseline_model1b_reg_stats
```

# GAD retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad education sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# PHQ retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq education sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# OCIR retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```

# OCIR prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir education sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```

# PCL baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivity model1b absolute whole sample}
# Regression coefficients
pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
                                                 data_set = "dat")
kable(pcl_baseline_model1b_estimates)
pcl_baseline_model1b_estimates

#PCL prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r pcl education sensitivty model1b sum_score prepan}
# Regression coefficients
pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_estimates)
pcl_prepan_model1b_education_estimates

# Regression diagnostic statistics
pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(pcl_prepan_model1b_education_reg_stats)
pcl_prepan_model1b_education_reg_stats
```

# Sensitivity anlayses based on employment prior to covid
# Function change to include employment prior to covid as predictors

```{r model1b employment prior covid function}
model1b.estimates <- function(outcome, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c("depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
                                )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
               "employment_prior_covidEmployed" = "Employed",
               "employment_prior_covidUnemployed" = "Unemployed",
               "employment_prior_covidRetired" = "Retired",
               "employment_prior_covidStudent" = "Student"

```{r model1b.explan employment prior covid function}
model1b.explan.estimates <- function(outcome, explan_var, data_set) {
  # define the variable name of the dependent variable
  dependent.variable <- outcome
  # define the independent variables
  independent.variables <- c(explan_var,
                             "depression_and_anxiety",
                             "eating_disorders",
                             "obsessive_compulsive_disorders",
                             "bipolar_and_schizophrenia",
                             "mhd.posttraumatic_stress_disorder_ptsd",
                             "autism_spectrum_disorder",
                             "mhd.attention_deficit_hyperactivity_disorder",
                             "mhd.personality_disorder",
                             "Gender_collapsed",
                             "age_category_collapsed",
                             "Ethnicity_collapsed",
                             "key_worker",
                             "time_diff_coping_lockdown_march_23",
                             "employment_prior_covid"
  )
  # create the formula
  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
  glm.formula
               "age_category_collapsed19-25" = "19-25 years",
               "age_category_collapsed26-35" = "26-35 years",
               "age_category_collapsed36-45" = "36-45 years",
               "age_category_collapsed46-55" = "46-55 years",
               "age_category_collapsed56-65" = "56-65 years",
               "age_category_collapsed66-70" = "66-70 years",
               "age_category_collapsed71-75" = "71-75 years",
               "age_category_collapsed76+" = "76+ years",
               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
               "employment_prior_covidEmployed" = "Employed",
               "employment_prior_covidUnemployed" = "Unemployed",
               "employment_prior_covidRetired" = "Retired",
               "employment_prior_covidStudent" = "Student"

# GAD baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_estimates)
gad_baseline_model1b_estimates

# Regression diagnostic statistics
gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
                                                 data_set = "dat")
kable(gad_baseline_model1b_reg_stats)
gad_baseline_model1b_reg_stats
```

# GAD retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# GAD prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_estimates)
gad_prepan_model1b_education_estimates

# Regression diagnostic statistics
gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(gad_prepan_model1b_education_reg_stats)
gad_prepan_model1b_education_reg_stats
```

# PHQ baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
                                                 data_set = "dat")
kable(phq_baseline_model1b_estimates)
phq_baseline_model1b_estimates

# PHQ retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# PHQ prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_estimates)
phq_prepan_model1b_education_estimates

# Regression diagnostic statistics
phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(phq_prepan_model1b_education_reg_stats)
phq_prepan_model1b_education_reg_stats
```

# OCIR baseline
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b absolute whole sample}
# Regression coefficients
ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
                                                 data_set = "dat")
kable(ocir_baseline_model1b_estimates)
ocir_baseline_model1b_estimates

# OCIR retro
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score retro}
# Regression coefficients
ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_estimates)
ocir_retro_model1b_explan_estimates

# Regression diagnostic statistics
ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                                                               explan_var = "ocir.sum_score_retro",
                                                               data_set = "dat.retro")
kable(ocir_retro_model1b_explan_reg_stats)
ocir_retro_model1b_explan_reg_stats
```

# OCIR prepan
### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r ocir employment prior covid sensitivity model1b sum_score prepan}
# Regression coefficients
ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_estimates)
ocir_prepan_model1b_education_estimates

# Regression diagnostic statistics
ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
                         explan_var = "pcl.sum_score_prepan",
                         data_set = "dat.prepan")
kable(ocir_prepan_model1b_education_reg_stats)
ocir_prepan_model1b_education_reg_stats
```
